---
title: "Assignment 1"
author: "ningze zu"
date: "September 17, 2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Document assignment

```{r}
cover_url = 'https://elgarblog.files.wordpress.com/2013/10/books1.jpg'
if (!file.exists(cover_file <- 'cover.jpg'))
  download.file(cover_url, cover_file, mode = 'wb')
knitr::include_graphics(if (identical(knitr:::pandoc_to(), 'html')) cover_url else cover_file)
```


Consider the following situation:  

A sloppy printer produces books with an average of 2 misprints per page. You want to
know how many pages in a 50 page book will have more than k misprints. Make an n x k table that shows the probability that n or fewer pages in a 50 page book will have more than k misprints.  

Show and explain your work.  Include equations and calculations to teach the reader how to solve the problem.  Include an image of a book.

Push your solution to a github repository and submit the url for repository on blackboard.
Be sure your repo includes your document as a pdf file and as an RMD file.  Include other files needed to recompile your document.

Please keep in mind that the purpose of this assignment is to produce a document.  The problem was SUPPOSED to be easy.

Given that the stated mean value of 2 misprints per page, assume the distribution of $X$, the number of misprints of per page is a Poisson distribution $P(\lambda)$ with $\lambda=2$. The PDF of poisson distribution is $$P(X>k)=\frac{{e^{ - \lambda } \lambda ^x }}{{x!}}$$
Conditioned on $k$, the probability $p_k$ of or more than $k$ misprints on a page is: $$p_k=P(X>k)=1-P(X\leqslant k)=1-ppois(k, \lambda=2)$$
Then we have the table of the probability that n or
fewer pages in a 50 page book will have more than k misprints.
```{r}
library(knitr)
n=50
k=10
prob <-matrix(ncol = k+1, nrow=n)
for (i in 1:n){
  for (j in 0:k){
    p = ppois(j, 2, lower.tail = TRUE)
    prob[i,j+1]=dbinom(i,50, prob = (1-p))
  }
  prob
}
prob = as.data.frame(prob)
colnames(prob)=paste0("k=", c(0:10))
rownames(prob)=paste0("n=", c(1:50))
kable(prob)
```

